---
title: "Rbookdown"
author: "cui219"
date: "2020/3/27"
output:
  html_document:
    df_print: paged
---

##Consider approximation of the distribution function of $N(0, 1)$

$\Phi(t) = \int_{-\infty}^t \frac{1}{\sqrt{2\pi}} e^{-y^2 / 2}dy$,

##$$the Monte Carlo methods:

$\hat\Phi(t) = \frac{1}{n} \sum_{i=1}^n I(X_i \le t)$

where $X_i$'s are a random sample from $N(0, 1)$, and $I(\cdot)$ is the indicator function. Experiment with the approximation at $n \in \{10^2, 10^3, 10^4\}$ at  $t \in \{0.0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72\}$form a table.

```{r}

t = c(0, 0.67, 0.84, 1.28, 1.65, 2.32, 2.58, 3.09, 3.72)
n = c(100, 1000, 10000)
p = matrix(0, nrow=9, ncol=3)
a = 0
for(i in 1:9)
  for(j in 1:3){
    a = a+1
    num = rnorm(n[j], 0, 1)
    p[i, j] = mean(num<t[i])
    print(a)
  }
rownames(p)<-t
colnames(p)<-n

library(knitr)
library(magrittr)
library(kableExtra)
library(callr)
library(webshot)

kable(p, booktabs=TRUE, caption='(ref:norm)') %>% 
 kable_styling(bootstrap_options = "striped",full_width = F) %>% 
 column_spec(1,bold=T)
```

The table should include the true value for comparison.
Further, repeat the experiment 100 times. 
Draw box plots of the 100 approximation errors at each $t$ using **ggplot2** [@R-ggplot2] for each $n$.

```{r}
x=pnorm( c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE )
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^2
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + 
  geom_boxplot() + 
  scale_x_continuous(breaks=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)) + 
  labs(title="Figure 1: the box plot of the 100 approximation errors (n=10^2)",y="error",
       x="t") + 
  theme(plot.title=element_text(size=9,hjust=0.3))  
```

```{r}
x=pnorm( c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE )
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^3
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(q,aes(T,X,group=T)) + 
  geom_boxplot() + 
  scale_x_continuous(breaks=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)) + 
  labs(title="Figure 2: the box plot of the 100 approximation errors (n=10^3)",y="error",
       x="t") + 
  theme(plot.title=element_text(size=9,hjust=0.3))
```

```{r}
x=pnorm( c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72), mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE )
t=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)
n=10^4
z=matrix(0,100,9)
w=matrix(0,9,n)
for(p in 1:100)
{ y=c(rnorm(n,mean=0,sd=1))
  for(k in 1:9)
  {
   for(j in 1:n)
  {w[k,j]=sign(y[j]<=t[k])}
z[p,k]=sum(w[k,])/n}}
z=as.data.frame(z)
r=c(z$V1,z$V2,z$V3,z$V4,z$V5,z$V6,z$V7,z$V8,z$V9)
e=c(rep(0.0,100),rep(0.67,100),rep(0.84,100),rep(1.28,100),rep(1.65,100),rep(2.32,100),rep(2.58,100),rep(3.09,100),rep(3.72,100))
q=data.frame(T=rep(0,100),X=0)
for(s in 1:900)
{q[s,2]=r[s]}
for(s in 1:900)
{q[s,1]=e[s]}
for(a in 1:100)
 { q[a,2]=q[a,2]-x[1]
 q[a+100,2]=q[a+100,2]-x[2]
 q[a+200,2]=q[a+200,2]-x[3]
 q[a+300,2]=q[a+300,2]-x[4]
 q[a+400,2]=q[a+400,2]-x[5]
 q[a+500,2]=q[a+500,2]-x[6]
 q[a+600,2]=q[a+600,2]-x[7]
 q[a+700,2]=q[a+700,2]-x[8]
 q[a+800,2]=q[a+800,2]-x[9]}
library(ggplot2)
ggplot(data=q,aes(x=T,y=X,group=T)) + 
  geom_boxplot() + 
  scale_x_continuous(breaks=c(0.0,0.67, 0.84,1.28,1.65,2.32,2.58,3.09,3.72)) + 
  labs(title="Figure 1: the box plot of the 100 approximation errors (n=10^4)",y="error",
       x="t") + 
  theme(plot.title=element_text(size=9,hjust=0.3))
```


